Jane, John … Leslie? A Historical Method for Algorithmic Gender Prediction

### 2015-08-21 article.Rmd
Sharpen do-nothing critique and citation to Eckert

Nevertheless, the methodology that we have described here does take advantage of the datasets available to historians. The predictions it provides are not intended to be taken as the entirety of what historians can say about gender in the past. But they provide the ability to uncover data about gender where it was previously unknown, thus providing further grist to the mill of more traditional methods. Furthermore, the gender package is entirely open-source, and we have provided detailed documentation for its code and underlying data so that researchers who wish to build upon it can modify the package accordingly. By building as much flexibility and transparency into the method as possible, we hope that others can continue to make just these kinds of improvements.

@@

>>>>

Nevertheless, the methodology that we have described here does take advantage of the datasets available to historians. While we agree with the category of critique that we have cited, we do not think that they should deter scholars from making use of our method. While such critiques point out genuine problems, they also seldom contain concrete proposals that can actually be implemented in historical research.^[Discussing exactly this problem of gender/sex binaries in large corpora, Penelope Eckert argues that "binary sex-class gets us pretty far" and argues that "at the moment" it is not "whether there's any way we can code large corpora for something subtler about gender than sex 
class" [Eckert 2012].] The predictions that our method provides are by no means intended to be taken as the entirety of what historians can say about gender in the past. But they do provide the ability to uncover data about gender where it was previously unknown, thus providing further grist to the mill of more traditional methods. Furthermore, the gender package is entirely open-source, and we have provided detailed documentation for its code and underlying data so that researchers who wish to build upon it can modify the package accordingly. By building as much flexibility and transparency into the method as possible, we hope that others can continue to make just these kinds of improvements.

@@

[Eckert 2012] Eckert, Penelope. "Coding for Gender and Sexuality." NSF-LDC workshop on coding sociolinguistic corpora. LSA Annual Meeting, Portland (2012). <https://www.ldc.upenn.edu/sites/www.ldc.upenn.edu/files/eckert-paper.pdf>.
